Autocorrelation in Sparse Distributed Memory

### 2018-11-09 paperIEEE.tex
Alignment respecting column borders
Photo 2

%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twocolumn,journal]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{calc}
\usepackage{graphicx}
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}
\hypersetup{pdftitle={Your Title},
 pdfauthor={Your Name},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}

@@

 \usepackage[round, numbers]{natbib}

@@

\markboth{Working Paper}{Brogliato and Linhares: Autocorrelation of SDM}

@@

\begin{IEEEbiography}[{\fbox{\begin{minipage}[t][1.25in]{1in}%
Replace this box by an image with a width of 1\,in and a height of
1.25\,in!%
\end{minipage}}}]{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published circa 30 papers in journals such as \emph{Artificial Intelligence, Biological Cybernetics, Cognitive Science, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Psychology,} etc.
\end{IEEEbiography}

>>>>

%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twocolumn,journal]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{calc}
\usepackage{graphicx}
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}

\hypersetup{pdftitle={Your Title},
 pdfauthor={Your Name},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}

@@

 \usepackage[round, numbers]{natbib}
 \bibliographystyle{unsrtnat}

@@

\markboth{Working Paper}{Brogliato and Linhares: Autocorrelation in SDM}

@@

%\begin{IEEEbiography}[{\fbox{\begin{minipage}[t][1.25in]{1in}{Linhares.jpg}

\begin{IEEEbiography}[
  {
  \includegraphics[width=1in,height=1.25in,clip]{./Chapters/Linhares.jpg}
  }
  ]
{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published ~30 papers in journals such as \emph{Artificial Intelligence, Biological Cybernetics, Cognitive Science, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Human Neuroscience,} etc.
\end{IEEEbiography}
